QPLIB: A Library of Quadratic Programming Instances

### 2017-01-24 QPLIB-2.2.tex
revise instance selection section
- add some todos
- fix spelling and grammar
revise conclusions and appendix

Our taxonomy is based on a three-fields code of the form ``\textit{OVC}'', where \textit{O} indicates the objective function, \textit{V} the variables, and \textit{C} the constraints of the problem. The fields can be given the following values:
%
\begin{itemize}
 \item objective function: (L)inear, (D)iagonal convex quadratic, (C)onvex quadra-tic, nonconvex (Q)uadratic;
 %
 \item variables: (C)ontinuous only, (B)inary only, (M)ixed binary and continuous, (I)nteger only, (G)eneral (all three types);
 %
 \item constraints: (N)one, (B)ox, (L)inear, (D)iagonal convex quadratic, (C)onvex quadratic, nonconvex (Q)ua-dratic.
\end{itemize}
%
The wildcard ``*'' will be used to indicate any possible choice, and lists of the form ``\{X, Y, Z\}'' will indicate that the value of the given field can freely attain any of the specified values.

@@

  \item \emph{Nonconvex Integer Quadratic Programs} QGQ is the most general, and therefore is the most difficul, class. Due to the lack of convexity even when integrality requirements are removed, solution methods must typically combine several algorithmic ideas, such as enumeration (distinguishing the role of integral variables from that of continuous ones involved into nonconvex terms) and techniques (e.g., outer approximation, SDP relaxation, \ldots) that allow to efficiently compute bounds. As in the convex case, QBQ, QMQ, and QIQ can benefit from more specific properties of the variables \cite{Buchheim2013,Dong2016}\todo{citations?}.

>>>>

Our taxonomy is based on a three-fields code of the form ``\textit{OVC}'', where \textit{O} indicates the objective function, \textit{V} the variables, and \textit{C} the constraints of the problem. The fields can be given the following values:
%
\begin{itemize}
 \item objective function: (L)inear, (D)iagonal convex quadratic, (C)onvex quadra-tic, nonconvex (Q)uadratic;
 %
 \item variables: (C)ontinuous only, (B)inary only, (M)ixed binary and continuous, (I)nteger only, (G)eneral (all three types\todo{or mixed integer and continuous?});
 %
 \item constraints: (N)one, (B)ox, (L)inear, (D)iagonal convex quadratic, (C)onvex quadratic, nonconvex (Q)ua-dratic.
\end{itemize}
%
The wildcard ``*'' will be used to indicate any possible choice, and lists of the form ``\{X, Y, Z\}'' will indicate that the value of the given field can freely attain any of the specified values.

@@

  \item \emph{Nonconvex Integer Quadratic Programs} QGQ is the most general, and therefore is the most difficul, class. Due to the lack of convexity even when integrality requirements are removed, solution methods must typically combine several algorithmic ideas, such as enumeration (distinguishing the role of integral variables from that of continuous ones involved into nonconvex terms) and techniques (e.g., outer approximation, semidefinite programming relaxation, \ldots) that allow to efficiently compute bounds. As in the convex case, QBQ, QMQ, and QIQ can benefit from more specific properties of the variables \cite{Buchheim2013,Dong2016}\todo{citations?}.

### 2017-01-24 conclusion.tex
revise conclusions and appendix

 This manuscript describes the first comprehensive library of instances for Quadratic Programming (QP). Since QP comprises  different and `varied'' categories of problems, we propose a classification and then we describe the principal solution methods representing the state-of-the-art algorithms for QP.

>>>>

 This manuscript describes the first comprehensive library of instances for Quadratic Programming (QP). Since QP comprises  different and ``varied'' categories of problems, we propose a classification and then we describe the principal solution methods representing the state-of-the-art algorithms for QP.
